Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Fixed some errors

Seek time; which is the time it takes for the Read-Write to move up and down the platter.
The Seek time itself is comprised of a series of phase times. The first being the acceleration phase,
the read write arm starts to move, then comes the coasting phase when the arm is moving at full speed. This
is followed by the deceleration phase where the read write arm slows down. Then finally comes the
settling phase as the read write head stops right at the data it needs.
The average seek time of hardrives of size 300 GB to 1TB ranged from an average time of 4ms to 9ms.
(source: \cite{tbree} )

@@

In an extensive calculation done by Remzi Arpaci-Dusseau and Andrea Arpaci-Dusseau, in the \cite{tbree},
two hard drives one Cheetah, and the other being Barracuda was compared for the I/O latency time. The size of
data being dealt with was 100 MB. However, another controller in the comparison was whether the data reading or writing
was sequential or random. Sequential meant that large chunks of data are just being read and written which are in
sequence, whereas the Random transfer just meant Random data was selected from a read issue some where on the disk,
which is how the data for applications work. Mind it that the data we represented in the simulator was also sequential
and not random, as the hardrive implemented was built of data blocks.

The I/O Latency time along with other statistics mentioned above was (taken from the source \cite{tbree}):

@@

Not all of this information, especially concerning network is that closely relevant to our field of study, but
we can certianly see the latencies that included reading, writing and referencing from the CPU caches, memory
and the drives had a huge difference in between them. The low level operations that took place within the
CPU were the quickest of all, referencing Caches and branching. Secondly referencing the RAM (7 ns) was slower than
referencing the the caches (0.5 ns & 7 ns but alot faster that going to a and reading from disk which was almost a
20 million times slower than refernecing the L1 Cache and upto a hundred thousand times slower than referencing
the RAM.

>>>>

Seek time; which is the time it takes for the Read-Write to move up and down the platter.
The Seek time itself is comprised of a series of phase times. The first being the acceleration phase,
the read write arm starts to move, then comes the coasting phase when the arm is moving at full speed. This
is followed by the deceleration phase where the read write arm slows down. Then finally comes the
settling phase as the read write head stops right at the data it needs.
The average seek time of hardrives of size 300 GB to 1TB ranged from an average time of 4ms to 9ms.
(source: \cite{three} )

@@

In an extensive calculation done by Remzi Arpaci-Dusseau and Andrea Arpaci-Dusseau, in the \cite{three},
two hard drives one Cheetah, and the other being Barracuda was compared for the I/O latency time. The size of
data being dealt with was 100 MB. However, another controller in the comparison was whether the data reading or writing
was sequential or random. Sequential meant that large chunks of data are just being read and written which are in
sequence, whereas the Random transfer just meant Random data was selected from a read issue some where on the disk,
which is how the data for applications work. Mind it that the data we represented in the simulator was also sequential
and not random, as the hardrive implemented was built of data blocks.

The I/O Latency time along with other statistics mentioned above was (taken from the source \cite{three}):

@@

Not all of this information, especially concerning network is that closely relevant to our field of study, but
we can certianly see the latencies that included reading, writing and referencing from the CPU caches, memory
and the drives had a huge difference in between them. The low level operations that took place within the
CPU were the quickest of all, referencing Caches and branching. Secondly referencing the RAM (7 ns) was slower than
referencing the the caches (0.5 ns and 7 ns) but alot faster that going to a and reading from disk which was almost a
20 million times slower than refernecing the L1 Cache and upto a hundred thousand times slower than referencing
the RAM.
